\section{SAST Audit Trail Crawling}
The Checkmarx SAST product contains some SQL tables where audit logging is stored.  For on-premise instance of SAST, it is possible to
configure CxAnalytix to crawl the audit tables found in the CxDB and CxActivity databases.  For this feature 
to work, a direct database connection must be made to the CxSAST DB.\footnote{This feature is not available for Checkmarx hosted instance of SAST.}

\noindent\\The account used to connect to the CxSAST DB has the following requirements:

\begin{enumerate}
    \item The account should be mapped to the CxDB and CxActivity databases.
    \item The account shouid have the roles "public" and "db\_reader" for both the CxDB and CxActivity databases.
\end{enumerate}

The CxAnalytixService running on Windows can use SSPI to connect to the database if the CxAnalytixService is configured to execute using a 
service account that meets the above requirements.  The connection string in the \texttt{CxDB} configuration element must indicate that
integrated security is to be used when connecting to the database.


\subsection{SQL Database Connection Configuration}

The \texttt{CxDB} configuration element is optional.  It is only required if SAST audit table data is to be crawled.  If the
\texttt{CxDB} element is not found in the configuration, no attempt to crawl audit tables will be made.

\begin{xml}{CxDB}{\expandsenv\encrypts}{}
<CxDB 
    ConnectionString="<sql connection string>" 
    />
\end{xml}

\subsection{Audit Trail Record Name Mapping Configuration}

The \texttt{CxAuditTrailRecords} configuration element is optional.  The purpose of this element is to map the names of data
crawled from SQL database tables to the name of a record in the output module.  All attributes of \texttt{CxAuditTrailRecords}
are full names of tables in the CxDB or CxActivity database.

\noindent\\In the example XML below, the value assigned to each attribute is the name of the record storage location where the crawled 
data will be written.  If using MongoDB, for example, the values would correspond to collection names in the MongoDB database.

\noindent\\If \texttt{CxAuditTrailRecords} is not provided in the configuration, the default name values are the same
as shown in the XML example below.

\begin{xml}{CxAuditTrailRecords}{}{}
<CxAuditTrailRecords
    CxDB.accesscontrol.AuditTrail="RECORD_CxDBaccesscontrolAuditTrail"
    CxActivity.dbo.AuditTrail="RECORD_CxActivitydboAuditTrail"
    CxActivity.dbo.Audit_DataRetention="RECORD_CxActivitydboAuditDataRetention"
    CxActivity.dbo.Audit_Logins="RECORD_CxActivitydboAuditLogins"
    CxActivity.dbo.Audit_Presets="RECORD_CxActivitydboAuditPresets"
    CxActivity.dbo.Audit_Projects="RECORD_CxActivitydboAuditProjects"
    CxActivity.dbo.Audit_Queries="RECORD_CxActivitydboAuditQueries"
    CxActivity.dbo.Audit_QueriesActions="RECORD_CxActivitydboAuditQueriesActions"
    CxActivity.dbo.Audit_Reports="RECORD_CxActivitydboAuditReports"
    CxActivity.dbo.Audit_ScanRequests="RECORD_CxActivitydboAuditScanRequests"
    CxActivity.dbo.Audit_Scans="RECORD_CxActivitydboAuditScans"
    CxActivity.dbo.Audit_Users="RECORD_CxActivitydboAuditUsers"
    />
\end{xml}


\subsection{Audit Trail Record Suppressions Configuration}

By default, when the \texttt{CxDB} configuration element is found in the configuration, all audit trail tables are crawled.  The
optional \texttt{CxAuditTrailSupressions} configuration element allows some audit trail tables to be omitted from the crawl. 
All attributes of \texttt{CxAuditTrailSupressions} are full names of tables in the CxDB or CxActivity database.

\noindent\\By default, all audit trail tables are crawled.  The attribute value of "false" means the table will be crawled. The attribute
value of "true" means the table \textbf{will not} be crawled.\\

    
\begin{xml}{CxAuditTrailSupressions}{}{}
<CxAuditTrailSupressions
    CxDB.accesscontrol.AuditTrail="false"
    CxActivity.dbo.AuditTrail="false"
    CxActivity.dbo.Audit_DataRetention="false"
    CxActivity.dbo.Audit_Logins="false"
    CxActivity.dbo.Audit_Presets="false"
    CxActivity.dbo.Audit_Projects="false"
    CxActivity.dbo.Audit_Queries="false"
    CxActivity.dbo.Audit_QueriesActions="false"
    CxActivity.dbo.Audit_Reports="false"
    CxActivity.dbo.Audit_ScanRequests="false"
    CxActivity.dbo.Audit_Scans="false"
    CxActivity.dbo.Audit_Users="false"
    />
\end{xml}
