\chapter{Quickstart}

CxAnalytix performs read-only operations using Checkmarx REST APIs to obtain vulnerability data. It is therefore possible to execute 
CxAnalytix locally (e.g. on your workstation\footnote{Depending on the number of scans that need to be crawled, you may need a significant amount of disk space.}) 
or on a test system without the need to make any production changes.\\

\noindent The requirements to execute a test crawl are:

\begin{enumerate}
    \item Download the \href{https://github.com/checkmarx-ts/CxAnalytix/releases}{latest release zip}
    \item Unzip the release binaries into a directory of your choice
    \item Update the configuration with:
    \begin{itemize}
        \item The URL of the REST API endpoint(s)
        \item Credentials to access the REST API endpoint(s)
    \end{itemize}    
\end{enumerate}


\section{Quick SAST Crawl}


Some basic configuration is required before execution.

\begin{enumerate}
    \item Open a command prompt.
    \item Switch to the directory containing the CxAnalytix binaries.
    \item Set the environment variable \verb|CHECKMARX_URL| to the URL of your SAST instance.\footnote{Do not include "cxwebclient" in your SAST URL!}
    \item Set the environment variable \verb|CHECKMARX_USERNAME| to a SAST application user account name.
    \item Set the environment variable \verb|CHECKMARX_PASSWORD| to the password for the SAST application user account.
    \item Set the environment variable \verb|CHECKMARX_STATE_PATH| to a path where the state data will be stored.  
    A path of \verb|.| or any other temporary storage location is sufficient for evaluation.
    \item Execute \verb|CxAnalytixCLI| (Linux) or \verb|CxAnalytixCLI.exe| (Windows)
\end{enumerate}

The SAST vulnerability data will be retrieved and written to files in the \verb|logs| directory located in the directory where the CxAnalytix binaries
have been extracted.  If the crawl is interrupted, it will be re-started from the scan being processed when the crawl was interrupted.  To completely 
re-start the crawl, find and delete the \verb|CxAnalytixExportState.json| file in the directory specified by the \verb|CHECKMARX_STATE_PATH| 
environment variable.
