\section{2.0.1}

\subsection*{FEATURES}
    \begin{itemize}
        \item Issue \#129 - New record type: scan statistics\\
		\indent A scan statistics record type has been added for optionally storing the scan statistics for SAST 9.4+ scans.
	
        \item Issue \#157 - include branching information for projects in CxAnalytix
		\indent Added fields in the Project Information Record:
        \begin{itemize}
			\item IsBranched
			\item BranchedAtScanId
			\item BranchParentProject
        \end{itemize}
			
	    \item Issue \#182 - Scan custom fields\\
		\indent Scan custom fields, if available, are now exported in the scan summary record.    
    \end{itemize}

\subsection*{UPDATES}
    \begin{itemize}
        \item Additional fields added to some records to aid in filtering when record types include records from multiple Checkmarx products.  
        This includes but is not limited to:
        \begin{itemize}
            \item ScanProduct
            \item ScanType
        \end{itemize}
        \item Issue \#93 - Documentation update regarding decrypting configuration sections encrypted by another user
    \end{itemize}

\subsection*{BUG FIXES}
    \begin{itemize}
        \item Issue \#158 - SAST scan summary totals should match the project state totals
        \item Issue \#183 - Audit table crawl throws an exception if the connection string is not defined
        \item Issue \#184 - Authentication issue - can't use disposed object
    \end{itemize}


\section{2.0.0}

\subsection*{FEATURES}
    \begin{itemize}
        \item Issue 12 - SCA compatibility
        \begin{itemize}
            \item The data field specification reflects data fields used by OSA and/or SCA.  The data concepts in OSA and SCA 
            are slightly different, thus the data fields will reflect these differences.
        \end{itemize}
    \end{itemize}

\subsection*{UPDATES}
    \begin{itemize}
        \item Using .Net 6.0
            \begin{itemize}
                \item Standalone execution has been supported for several versions, it is now the default.  A separate installation of .Net Core is no longer required.
            \end{itemize}
        \item Configuration file is now `cxanalytix.config` for all executables.
        \item Configuration file search path has changed to allow for easier upgrades.
        \item Configuration format for 2.x is not backwards compatible with 1.x configuration files.  Users of CxAnalytix prior to version 2.x will need 
        to create a new configuration file.
        \item Transformers are now pluggable modules that must be selected in the configuration.
        \item Outputs have always been pluggable modules, but selection is now more user friendly.
    \end{itemize}

\subsection*{BUG FIXES}
    \begin{itemize}
        \item Garbage collection tuning.
    \end{itemize}


\section{1.3.3}
\subsection*{BUG FIXES}
    \begin{itemize}
        \item Performance fix - throttle the API I/O calls during scan crawl resolution to use only the configured number of concurrent threads.
        \item Issue 142 - Correct the SinkFileName, SinkLine, SinkColumn values in the scan detail output.
        \item Issue 135 - Avoid repeatedly calling OSA endpoints if OSA is not licensed.
        \item Issue 109 - The user agent now shows API requests with CxAnalytix and version in the user agent string.
    \end{itemize}

\subsection*{UPDATES}
    \begin{itemize}
        \item As of v1.3.3, CxAnalytix is no longer compatible with SAST versions prior to 9.0.
    \end{itemize}

\section{1.3.2}
\subsection*{BUG FIXES}
    \begin{itemize}
        \item Memory leak in M\&O client REST API code fixed.
        \item Added the `RetryLoop` configuration to allow retries after timeout.
        \item Stopped the attempt to load policies at startup if the M\&O URL is not provided.
        \item Stability fixes for AMQP outputs.
        \item Dependency upgrades.
        \item Garbage collection tuning.
    \end{itemize}


\section{1.3.1}
\subsection*{FEATURES}
    \begin{itemize}
        \item Platform-specific tarballs are now created.  This is to address the dynamic loading of DPAPI that .Net Core apparently doesn't handle well in cross-platform builds.
        \item Pseudo-transactions are now off by default.
        \item New data fields added to scan summary and scan detail records.
    \end{itemize}

\subsection*{BUG FIXES}
    \begin{itemize}
        \item Issue 85 - Malformed AMQP config written on first run, preventing subsequent runs without removing the malformed config and commenting out the AMQP config class references.
    \end{itemize}


\section{1.3.0}
\subsection*{FEATURES}
    \begin{itemize}
        \item Issue 10 - Output can now be routed to AMQP endpoints
    \end{itemize}


\section{1.2.5}
\subsection*{FEATURES}
    \begin{itemize}
        \item Issue 52 - Transactional writes have been implemented as Pseudo Transactions.
    \end{itemize}

\subsection*{BUG FIXES}
    \begin{itemize}
        \item An issue with crawls aborting on SAST systems not licensed for OSA was re-introduced in 1.2.2 and has been fixed.
    \end{itemize}

\section{1.2.4}
\subsection*{BUG FIXES}
    \begin{itemize}
        \item Stability fix for cases where M\&O did not return policy violations as expected
        \item Build change to not build self-contained; this was causing issues on some Linux distros
    \end{itemize}


\section{1.2.3}
\subsection*{FEATURES}
    \begin{itemize}
        \item Issue 57 - Filtering scans crawled via Team and Project regex matching
    \end{itemize}
\subsection*{BUG FIXES}
    \begin{itemize}
        \item Issue 17 - Updated the docker image to better support persisting the state files
    \end{itemize}


\section{1.2.2}
\subsection*{FEATURES}
    \begin{itemize}
        \item Fields added to the output records
        \begin{itemize}
            \item Project Information
            \begin{itemize}
                \item LastCrawlDate
            \end{itemize}
        \end{itemize}
        \begin{itemize}
            \item Policy Violation Details
            \begin{itemize}
                \item ViolationId
            \end{itemize}
        \end{itemize}
        \item A basic [regression testing utility](https://github.com/checkmarx-ts/CxAnalytix/wiki/Development-Home) was added to test that data extraction is consistent between versions.  This is primarily targeted for developer use.
    \end{itemize}

\subsection*{BUG FIXES}
    \begin{itemize}
        \item Issue 51 - Timestamp of date to check for last scan is recorded as the finish date of the last scan found during the current crawl rather than the date of the current crawl.
        \item Issue 53 - Authorization token refresh improvements
        \item Stealth fix during development - NodeLine would be excluded from the SAST Vulnerability Details record under certain conditions 
    \end{itemize}


\section{1.2.1}
\subsection*{BUG FIXES}
    \begin{itemize}
        \item Issue 60 - A DB table row with a column containing a NULL value threw an exception and caused the DB crawl to end prematurely.
    \end{itemize}


\section{1.2.0}
\subsection*{FEATURES}
    \begin{itemize}
        \item New feature to extract audit events by crawling audit log tables in CxActivity and CxDB.  This feature is limited to use in systems that can make a connection directly to the CxSAST DB.
    \end{itemize}

\section{1.1.7}
\subsection*{BUG FIXES}
    \begin{itemize}
        \item Issue 31 - No time delay between queries for report generation status.
    \end{itemize}


\section{1.1.6}
\subsection*{BUG FIXES}
    \begin{itemize}
        \item Issue 26 - OSA scan details incomplete or missing
    \end{itemize}
\subsection*{FEATURES}
    \begin{itemize}
        \item The rolling file log naming convention should cause daily log rotation as well as 100MB max log file sizes by default.
    \end{itemize}

\section{1.1.5}
\subsection*{FEATURES}
    \begin{itemize}
        \item Added the ability to dump all network I/O to the application log.
        \item Improved error handling and exception logging for troubleshooting purposes.
    \end{itemize}
\subsection*{BUG FIXES}
    \begin{itemize}
        \item Issues 21, 22 - Networking implementation caused issues on some versions of Windows server.
    \end{itemize}


\section{1.1.4}
\subsection*{FEATURES}
    \begin{itemize}
        \item Added EngineStart/EngineFinished fields to the scan summary; no-change scans will be indicated with DateTime.MinValue
    \end{itemize}
\subsection*{BUG FIXES}
    \begin{itemize}
        \item Issue 20: Date parsing error in non-US locale
    \end{itemize}

\section{1.1.3}
\subsection*{BUG FIXES}
    \begin{itemize}
        \item Issue 18: Error when attempting to retrieve policy violation data from SAST 9.0
    \end{itemize}


\section{1.1.2}
\subsection*{FEATURES}
    \begin{itemize}
        \item Dockerfile now available as a release artifact
        \item Docker base image pushed to Docker Hub as part of the build 
    \end{itemize}

\section{1.1.1}
\subsection*{FEATURES}
    \begin{itemize}
        \item Issue 9: Resolve config values from environment variables (see the Wiki for [CxConnection](https://github.com/checkmarx-ts/CxAnalytix/wiki/CxConnection), [CxCredentials](https://github.com/checkmarx-ts/CxAnalytix/wiki/CxCredentials), and [CxAnalyticsService](https://github.com/checkmarx-ts/CxAnalytix/wiki/CxAnalyticsService))
    \end{itemize}
\subsection*{BUG FIXES}
    \begin{itemize}
        \item Issue 6: Now compatible with SAST 9.0
    \end{itemize}

\section{1.1.0}
\subsection*{FEATURES}
    \begin{itemize}
        \item Issue 4: MongoDB is now available as an output destination.
        \item Issue 5: Add instance identifier to each record.
        \item Issue 7: Add project custom fields to the output.
    \end{itemize}

\section{1.0.0 - Initial Release}
\subsection*{FEATURES}
    \begin{itemize}
        \item Output to flat log files
        \item Support for CxSAST 8.9 APIs
    \end{itemize}
